### 2010-12-09 docs/tex/acknowledgment.tex
Page number issues for abstract and acknowledgment is fixed.

\begin{center}
\begin{large}
\textbf{Acknowledgement}
\end{large}
\end{center}
I really acknowledge..

>>>>

\newpage
\phantomsection \label{acknowledgements}
\addcontentsline{toc}{chapter}{\numberline{}Acknowledgment}

\begin{center}
\begin{large}
\textbf{Acknowledgements}
\end{large}
\end{center}
My first appreciation goes to my supervisor Dr. Peter Grogono. It is not only a privilege to work with him, but also the inspiration and encouragement that I have received from him during the period of this work, made it possible.

My second appreciation goes to my parents. Their hard work and sacrifice in life made it possible for me to be able to come all this way.

My third appreciation is to my sister, who also made it easier for me, to be able to give all the time that I required to complete my thesis.
